Lyman-alpha spectra from rotating outflows

### 2018-03-26 paper/paper.tex

\begin{figure*}
\begin{center}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_skw_vout5_logtau7}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_skw_vout25_logtau7}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_skw_vout50_logtau7}
  \end{center}
  \caption{\textbf{Skewness for RT and DS:} The triangles represent the Radiative 
    Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
    \label{fig:skewness}}
\end{figure*}

@@

% Esta figura deberia tener en el eje x theta y en el eje y intensity of valley
% cada panel tiene una curva para logtau = 5, 6, 7.
\begin{figure*}
\begin{center}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau5}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau6}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau7}
\end{center}
\caption{\textbf{Valley Intensity:} We show for each \tauh the dependency that
		the viewing angle $\theta$ has on the line's the valley intensity. The larger 
		$\cos{\theta}$ the lower is the valley intensity, so the higher $\theta$, the 
		higher the valley intensity. We fixed $\vout=5$\kms and $\vrot=100$\kms. 
		\label{fig:valley_intensity}}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout5_logtau7}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout25_logtau7}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout50_logtau7}
  \end{center}
  \caption{\textbf{Skewness for RT and DS:} The triangles represent the Radiative 
    Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
    \label{fig:skewness}}
\end{figure*}

@@

% Esta figura deberia tener en el eje x theta y en el eje y intensity of valley
% cada panel tiene una curva para logtau = 5, 6, 7.
\begin{figure*}
\begin{center}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau5}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau6}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau7}
\end{center}
\caption{\textbf{Valley Intensity:} We show for each \tauh the dependency that
		the viewing angle $\theta$ has on the line's the valley intensity. The larger 
		$\cos{\theta}$ the lower is the valley intensity, so the higher $\theta$, the 
		higher the valley intensity. We fixed $\vout=5$\kms and $\vrot=100$\kms. 
		\label{fig:valley_intensity}}
\end{figure*}
